Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-02-06 Ben_Manuscripts/structure_paper/supplemental.tex
got rid of thing

  \begingroup
	\fontsize{14pt}{12pt}\selectfont
	\textbf{Initial Configuration Dependence}
  \endgroup

  \vspace{1em}
  We addressed any major dependence on initial configuration in the main text.
  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
  monomers per layer. We also showed that systems are stable when monomer head
  groups are oriented in the parallel displaced and sandwiched configurations
  (See Figure~\ref{fig:stacking}). Our model best supports a system built with 5
  monomers per layer in the sandwiched configuration.

@@

  \vspace{1em}
  \begingroup
	\fontsize{14pt}{12pt}\selectfont
	\textbf{Experimental correlation length of Ri-$\pi$}
  \endgroup

  %Our model is insensitive to initial configuration if monomer placement is chosen within reason.

@@

	  We tested five different initial pore spacings, defined as the
	  distance between the central axis of each pore with all others. To reduce the
	  number of variables, we held the pore radius constant, at 6 \AA~and the
	  distance between layers at 3.7 \AA~since those were the values used in our
	  optimal system in the main text. If the initial pore spacing is chosen to be
	  too small, pore columns abruptly repel each other as soon as they are able to
	  overcome the restraining potential present as part of the dry equilibration
	  procedure. We avoided using systems that exhibit this behavior since the
	  behavior increases the chances of a system to become kinetically trapped in an
	  undesired metastable free energy basin.

@@

	  	\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to have a test system
		with an intial spacing below the experimental value. As soon as the restraining
		potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the columns are able to
		separate resulting in a large jump in pore spacing (Figure~\ref{fig:p2p_39}).

		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
		it closely matches the experimental pore spacing. Again, we observe abrupt
		repulsion of columns once the restraining potential is switched to 56 KJ
		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}).

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger than the
		experimental value. We observe relatively stable pore spacing during the
		restrained portion of the dry equilibration procedure
		(Figure~\ref{fig:p2p_45}). We chose to use this value for all our simulations
		in the main text.

		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \% larger than the
		experimental value. Once the restraining potential reaches 56 KJ mol$^{-1}$
		nm$^{-2}$, the pore spacing begins to decrease linearly (Figure~\ref{fig:p2p_50}).

		\item 55 \AA~: We tested a pore spacing of 55 \AA~ which is at
		a distance where monomers in each pore no longer intersect adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily.  The system equilibrates to a pore spacing of 4.27
		$\pm$ 0.06 nm.

@@

>>>>

  \vspace{1em}
  \begingroup
	\fontsize{14pt}{12pt}\selectfont
	\textbf{Experimental correlation length of R-$\pi$}
  \endgroup

  %Our model is insensitive to initial configuration if monomer placement is chosen within reason. 
  \begingroup
	\fontsize{14pt}{12pt}\selectfont
	\textbf{Initial Configuration Dependence}
  \endgroup

  \vspace{1em}
  We addressed any major dependence on initial configuration in the main text.
  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
  monomers per layer. We also showed that systems are stable when monomer head
  groups are oriented in the parallel displaced and sandwiched configurations
  (See Figure~\ref{fig:stacking}). Our model is most consistent with experiment
  when built with 5 monomers per layer, with layers stacked 3.7 \AA~apart in 
  the parallel displaced configuration.

@@

@@

	  We tested five different initial pore spacings, defined as the
	  distance between the central axis of each pore with all others
	  (Figure~\ref{fig:p2p_diagram}). To reduce the number of variables, we held the
	  pore radius constant, at 6 \AA~and the distance between layers at 3.7 \AA~since
	  those were the values used in our optimal system in the main text. We
	  prioritized ensuring that resulting configurations maintain the expected
	  hexagonal symmetry. If initial pore spacing is too small, we observe repulsion
	  between columns which disrupts equilibration. If the pore spacing is too large
	  the pores squeeze together, but in a distorted hexagonal array because the xy
	  translation of the pores is somewhat erratic.

%	  If the initial pore spacing is chosen to be
%	  too small, pore columns abruptly repel each other as soon as they are able to
%	  overcome the restraining potential present as part of the dry equilibration
%	  procedure. We avoided using systems that exhibit this behavior since the
%	  behavior increases the chances of a system to become kinetically trapped in an
%	  undesired metastable free energy basin.

@@

		\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
		have a test system with an intial spacing below the experimental value. As soon
		as the restraining potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the
		columns are able to repel resulting in a large jump in pore spacing
		(Figure~\ref{fig:p2p_39}). After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
		There is a large uncertainty in this value because the 1-4 pore spacing
		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
                towards cubic packing.

		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
		it closely matches the experimental pore spacing. Again, we observe abrupt
		repulsion of columns once the restraining potential is switched to 56 KJ
		mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). After 400 ns, the
		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
		spacings is 3.96 nm.

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
		than the experimental value. We observe relatively stable pore spacing during
		the restrained portion of the dry equilibration procedure
		(Figure~\ref{fig:p2p_45}). The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
		The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
		pore spacing. We chose to use this value for all our simulations in the main
		text.

		\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \% larger than the
		experimental value. Once the restraining potential reaches 56 KJ mol$^{-1}$
		nm$^{-2}$, the pore spacing begins to decrease linearly (Figure~\ref{fig:p2p_50}).
		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm. There is a large
                uncertainty with this value because, again, the array of pores deviates from 
                hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
                2 drifts outward from the array and forces the 1-4 distance to shrink in 
                response.

		\item 55 \AA~: We tested a pore spacing of 55 \AA~ which is at
		a distance where monomers in each pore no longer intersect adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily. The system equilibrates to a pore spacing of 4.27
		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
                spacing of 3.99 \AA~ which distorts the hexagonal array.

@@

	  \begin{figure}
		\centering
		\includegraphics[width=0.4\textwidth]{p2p_diagram.png}
		\caption{In a perfect hexagonal, there are 5 distances that should be exactly
		equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
		are the same.}~\label{fig:p2p_diagram}
	  \end{figure}
